### 2014-11-06 latex/phd_thesis.tex
Add comethylation chapter to thesis.
Discussion of Eckhardt et al.
Fixing up latex errors
Split co-methylation chapter.
Now split into “old stuff” (review of previous work) and “new stuff” (my work)
Updated Makefile to add new chapters
Updated Makefile
Removed unused macros

\documentclass[11pt,a4paper,oneside]{book}	%fleqn,

\usepackage{longtable,rotating,amsmath,epic, graphics}

@@

@@

% convenient macros for lists

\newcommand\BI{\begin{itemize}}

\newcommand\EI{\end{itemize}}

\newcommand\BE{\begin{enumerate}}

\newcommand\EE{\end{enumerate}}

\newcommand\BD{\begin{description}}

\newcommand\ED{\end{description}}

\newcommand\BF{\begin{figure}}

\newcommand\EF{\end{figure}}

\newcommand\BT{\begin{table}}

\newcommand\ET{\end{table}}

\newcommand\I\item

\newcommand\h[1]{\Large\textbf{#1}\vspace{12pt}}

\newcommand\N\newpage

\newcommand\BC{\begin{quotation}\small\noindent}

\newcommand\EC{\end{quotation}}

\newcommand\beq{\begin{equation}}

\newcommand\eeq{\end{equation}}

\newcommand{\ba}{{\bf a}}

\newcommand{\bb}{{\bf b}}

\newcommand{\bc}{{\bf c}}

\newcommand{\bd}{{\bf d}}

\newcommand{\be}{{\bf e}}

\newcommand{\bg}{{\bf g}}

\newcommand{\bh}{{\bf h}}

\newcommand{\bm}{{\bf m}}

\newcommand{\bn}{{\bf n}}

\newcommand{\bp}{{\bf p}}

\newcommand{\bq}{{\bf q}}

\newcommand{\br}{{\bf r}}

\newcommand{\bs}{{\bf s}}

\newcommand{\bt}{{\bf t}}

\newcommand{\bu}{{\bf u}}

\newcommand{\bv}{{\bf v}}

\newcommand{\bw}{{\bf w}}

\newcommand{\bx}{{\bf x}}

\newcommand{\by}{{\bf y}}

\newcommand{\bz}{{\bf z}}

\newcommand{\bC}{{\bf C}}

\newcommand{\bD}{{\bf D}}

\newcommand{\bH}{{\bf H}}

\newcommand{\bI}{{\bf I}}

\newcommand{\bM}{{\bf M}}

\newcommand{\bP}{{\bf P}}

\newcommand{\bT}{{\bf T}}

\newcommand{\bU}{{\bf U}}

\newcommand{\bV}{{\bf V}}

\newcommand{\bW}{{\bf W}}

\newcommand{\bX}{{\bf X}}

\newcommand{\bY}{{\bf Y}}

\newcommand{\bZ}{{\bf Z}}

\newcommand{\bone}{\mbox{\boldmath $1$}}

\newcommand{\balpha}{\mbox{\boldmath $\alpha$}}

\newcommand{\bbeta}{\mbox{\boldmath $\beta$}}

\newcommand{\bdelta}{\mbox{\boldmath $\delta$}}

\newcommand{\bepsilon}{\mbox{\boldmath $\epsilon$}}

\newcommand{\bgamma}{\mbox{\boldmath $\gamma$}}

\newcommand{\blambda}{\mbox{\boldmath $\lambda$}}

\newcommand{\bmu}{\mbox{\boldmath $\mu$}}

\newcommand{\bomea}{\mbox{\boldmath $\omega$}}

\newcommand{\bpi}{\mbox{\boldmath $\pi$}}

\newcommand{\bphi}{\mbox{\boldmath $\phi$}}

\newcommand{\brho}{\mbox{\boldmath $\rho$}}

\newcommand{\bsigma}{\mbox{\boldmath $\sigma$}}

\newcommand{\bSigma}{\mbox{\boldmath $\Sigma$}}

\newcommand{\btau}{\mbox{\boldmath $\tau$}}

\newcommand{\btheta}{\mbox{\boldmath $\theta$}}

\newcommand{\bpsi}{\mbox{\boldmath $\psi$}}

\newcommand{\bxi}{\mbox{\boldmath $\xi$}}

\newcommand{\bzeta}{\mbox{\boldmath $\zeta$}}

\newcommand{\bfeta}{\mbox{\boldmath $\eta$}}

\newcommand{\n}{\frac{1}{n}}

\newcommand{\E}{{\rm I\!E}}

\newcommand{\D}{{\rm I\!D}}

\newcommand{\R}{{\rm I\!R}}

\newcommand{\ls}{{\cal R}}

@@

\newcommand{\R}{{\textbf{\textsf{R}}}}}

@@

\BI

\I[(i)] the thesis comprises only my original work towards

@@

\I[(ii)] due acknowledgement has been made in

@@

\I[(iii)] the thesis is less than 100,000 words in length,

@@

\EI

@@

@@

>>>>

\documentclass[11pt,a4paper,oneside]{book}	%fleqn,
\usepackage{etex}

\usepackage{longtable,rotating, amsmath, epic, graphics, bm}

@@

\usepackage{booktabs}

@@

@@

\def\eqd{\,{\buildrel d \over =}\,}

%\newcommand{\R}{{\textbf{\textsf{R}}}}}

@@

\begin{itemize}

\item [(i)] the thesis comprises only my original work towards

@@

\item [(ii)] due acknowledgement has been made in

@@

\item [(iii)] the thesis is less than 100,000 words in length,

@@

\end{itemize}

@@

\include{biology_background} % biology_background.tex

@@

\include{avy} % avy.tex

\include{comethylation_review} % comethylation_review.tex

\include{comethylation} % comethylation.tex

\include{methsim} % methim.tex
